---
title: "RMarkdown ploty presentation"
author: "Abdul Rasheed Narejo"
date: "02/09/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

```{r, message = FALSE, echo=FALSE, warning=FALSE}
# load required libraries
library(plotly)
library(dplyr)
```

## Plot using plotly
```{r, echo = TRUE}
iris %>% plot_ly(x = ~Sepal.Length, y = ~Petal.Length, type="scatter",
        mode="markers", color = ~Species)
```

## added flexibility using ggplotly on ggplot graphs
```{r}
p <- ggplot(iris,aes(x=Sepal.Length,y=Sepal.Width, color = Species)) +
    geom_point() +
    stat_smooth(method="lm")

ggplotly(p)
```

## Source code
- The R Markdown source code of this presentation can be found in [this GitHub repository](https://github.com/arnarejo/CourseraDS-plotly).

